\section{Background}
\label{sec:background}

\subsection{Stage 1: 1D Estimation On a Fixed Axis}
The first stage of the estimation development was tracking the movement along a fixed axis. Using only the distance measurements from the beacons three stationary beacons to estimate the location and velocity.

\noindent The vehicles motion was modelled using a constant velocity method using the state vector \eqref{1D State Vector at t}. 
\begin{equation}
\label{1D State Vector at t}
    \mathbf{x}_t = \begin{bmatrix} p_t \\ v_t \end{bmatrix}
\end{equation}
Where $p_t$ is the position and $v_t$ is the velocity at a given time $t$.
\begin{equation}
\label{State dynamics matrix A}
    A = \begin{bmatrix} 1 & dt \\ 0 & 1 \end{bmatrix}
\end{equation}
The model does not contain a known control input such as throttle or breaking. The systems dynamics matrix A \eqref{State dynamics matrix A} controls the forward motion, Velocity is driven by the noise term $w_t$ \eqref{State update equation}.
\begin{equation}
\label{State update equation}
    x_{t+1} = \begin{bmatrix} 1 & dt \\ 0 & 1 \end{bmatrix} \cdot \begin{bmatrix} p_t \\ v_t \end{bmatrix} + \begin{bmatrix} 0 \\ 1 \end{bmatrix} w_t
\end{equation}
\begin{equation}
\label{State update equation simple}
    x_{t+1} = (A)(x_t) + w_t
\end{equation}
A standard Kalman filter is not suitable for this system due to the beacon data being non-linear. The sensors do not measure the vehicle coordinates but instead the Euclidean distance from the beacon \eqref{eq:location}.
\begin{equation} \label{eq:location}
    y_t = \sqrt{(p_t - p_{beacon})^2} + \nu_t
\end{equation}
The Extended Kalman Filter (EKF) process the non-linear distances using a Jacobian matrix. The Jacobian matrix calculates a flat tangent line that approximates the curve at a given time interval. Due to the nature of Jacobian it is only accurate for the current time stamp, it is required that the state variance remains small, if the variance is too large the EKF does not work.

\noindent Once the location data is linearised, the expected sensor measurement is calculated using equation \eqref{eq:ekf_update}.
\begin{equation} \label{eq:ekf_update}
    \hat{x}_{k|k} = \hat{x}_{k|k-1} + K_k \left( y_k - h(\hat{x}_{k|k-1}) \right)
\end{equation}
This equation takes the predicted location and adds a correction. The size of the correction is determined by the difference in the predicted sensor readings and the measured sensor, this is known as the residual. This residual is then multiplied by the Kalman gain, which scales the influence of the sensor correction on the final estimation. If the prediction is deemed reliable, the sensor correction is suppressed, allowing the physical model to drive the system.

\subsection{Stage 2: 2D Curvilinear Estimation}
The second stage of the estimation was to introduce the two dimensional
space, This allows for 4 degrees of freedom in the model, The vehicle can now
move and change velocity along X and Y axis.

\noindent The state vector is now \eqref{eq:state_vector_2d}, the
longitudinal and lateral locations (Px,Py) and the longitudinal and lateral velocities
(Vx,Vy).  
\begin{equation} \label{eq:state_vector_2d}
    \mathbf{x}_t = \begin{bmatrix} p_x \\ v_x \\ p_y \\ v_y \end{bmatrix}
\end{equation}

\noindent The system dynamics matrix is increased to a 4x4 matrix \eqref{eq:matrix_A_2d}, the Process
noise is applied only to the velocity terms. 
\begin{equation} \label{eq:matrix_A_2d}
    A = \begin{bmatrix} 
    1 & dt & 0 & 0 \\ 
    0 & 1 & 0 & 0 \\ 
    0 & 0 & 1 & dt \\ 
    0 & 0 & 0 & 1 
    \end{bmatrix}
\end{equation}

\noindent The mapping matrix G is used to distribute
the noise terms into the correct velocities \eqref{eq:update_2d}. The state update equation is \eqref{eq:update_2d}.
\begin{equation} \label{eq:G_matrix}
    \mathbf G = \begin{bmatrix} 0 & 0 \\ 1 & 0 \\ 0.1 & 0 \\ 0 & 1 \end{bmatrix} 
\end{equation}
\begin{equation} \label{eq:update_2d}
    \mathbf{x}_{t+1} = A\cdot G\cdot  \mathbf{w}_t
\end{equation}

\noindent The addition of the 2 dimensional space changes the measurement
method. as there is no longer a fixed y position, a minimum of three beacons is
required, to triangulate and estimate the vehicle location. The use of one
beacon places the location of the vehicle on a circle of circumference of
measured distance from vehicle to the beacon. If two beacons are used there
will be two locations where the circles overlap which are potential locations for
the vehicle to be at, the location where the vehicle is not is known as a ghost
location. The use of a third beacon pinpoints the location of the vehicle. The Euclidean
distance is measured between the car and the beacons \eqref{eq:measurement_2d}. 
\begin{equation} \label{eq:measurement_2d}
    h_i(\mathbf{x}_t) = \sqrt{(p_x - B_{x,i})^2 + (p_y - B_{y,i})^2}
\end{equation}

\noindent To handle the increased complexity of estimation model
CASADi is used, this allows for the partial derivatives in the Jacobian matrix
to be calculated using an algorithmic method, ensuring accuracy for each time point.

\noindent Due to the nature of random movement within 2 Dimensional
space hard coded boundaries were implemented \eqref{eq:constraints}. 
\begin{equation} \label{eq:constraints}
    \begin{aligned}
        -2 &\le p_y \le 2 \\
        0 &\le v_x \le 25 \\
        -0.55 &\le v_y \le 0.55
    \end{aligned}
\end{equation}
The track width was 4m to match
that of the racetrack. With boundary lines at 2 and -2 on y axis. This however
goes against the noise assumptions of a Gaussian distribution. Due to the estimation
being without the knowledge of the boundaries the filter may incorrectly estimate
the state variance.

\subsection{Stage 3: Curvilinear Estimation on a Circular Track}
The final stage of the initial development tracked the
vehicle and circular path. The system was expressed using curvilinear coordinates
to reduce the system complexity.

\noindent This allowed for the state vector to be reduced back to two
variables, arc position ($s_t$) and velocity ($v_{s,t}$) \eqref{eq:state_vector_arc}. 
\begin{equation} \label{eq:state_vector_arc}
    \mathbf{x}_t = \begin{bmatrix} s_t \\ v_{s,t} \end{bmatrix}
\end{equation}
The physical dynamics remain linear due to using the distance travelled along the curve as the $s$. The $A$ matrix used for the 1 dimensional estimator can be used again \eqref{eq:matrix_A_arc}.
\begin{equation} \label{eq:matrix_A_arc}
    A = \begin{bmatrix} 1 & dt \\ 0 & 1 \end{bmatrix}
\end{equation}

\noindent The estimator is unable to directly compare the predicted
arc length to the distance data collected form the beacons, to overcome this the
measured distance from the beacons is converted into Cartesian coordinates \eqref{eq:cartesian_mapping}. 
\begin{equation} \label{eq:cartesian_mapping}
    \begin{aligned}
        p_x &= R \cos\left(\frac{s_t}{R}\right) \\
        p_y &= -R \sin\left(\frac{s_t}{R}\right)
    \end{aligned}
\end{equation}
By using the known radius of the vehicle track. The sine transform is used to ensure positive
velocity is maintain clockwise around the track.

\noindent Once the cartesian plane is calculated Euclidean distance
can be calculated \eqref{eq:measurement_arc}. 
\begin{equation} \label{eq:measurement_arc}
    h_i(\mathbf{x}_t) = \sqrt{\left( R \cos\left(\frac{s_t}{R}\right) - B_{x,i} \right)^2 + \left( -R \sin\left(\frac{s_t}{R}\right) - B_{y,i} \right)^2}
\end{equation}
The use of CASADI allows for accuracy when calculating the
Jacobian matrix.