\section{Discussion}
\label{sec:disc}

Figure~\ref{fig:ekf-trajectory} demonstrates how a random walk for the state dynamics is not an appropriate physical model for the dyanamics of the system, as the lateral position is a random walk trajectory and is almost certain to escape the bounds of the system, which is only enforced through a hard clamp on the state variables.
This is further highlighted in Figure~\ref{fig:monte-carlo}, which also highlights the $2\sigma$ (standard deviation) for the path trajectories. It can be observed that all 3 relevant states of the system with constraints $(l, v_s, and v_l)$ escape their bounds.

There are several possible approaches to at least partially rectify this behaviour. A mean-reverting term\cite{uhlenbeck_1930_on} could be placed on the states to enforce soft constraints on the system:
\begin{equation}
\label{eq:mean-reversion}
    v_{t+1} = \alpha v_t + w_t
\end{equation}
Where $v_t$ is the velocity at time $t$, $w_t$ is a random gaussian noise term, and $\alpha$ is a scaling factor between 0 and 1. Given that the velocity in the system is only positive and initialised at 15 m/s, the velocity tajectoy will be scaled each step according to $\alpha$.

Additionally, a Gaussian truncation model\cite{burkardt_2023_the} could be utilised, constraining the domain of the distribution function depending on the lateral deviation from the centre point on the track.

\subsection{Limitations}
\label{sec:limitations}


\subsection{Future work}
\label{sec:future-work}
There is much potential for further enhancement of the system. These are outlined below in no paritcular order:

\begin{itemize}
    \item Further development of the system model with position uncertainty.
    \item Covariance terms in the position and velocity components.
    \item Expansion of the states to include appropriate vehicle model dynamics (i.e., unicycle model).
    \item Modelling the vehicle as a physical object with dimensions.
    \item Introduction of a deadzone around the edges of the track.
    \item An enhanced measurement model noise variance which scales with beacon distance.
    \item Including a additional bias terms in the measurement model (similar to the system dynamics, it becomes a measurement variable in the system).
    \item A small delay in the availability of the beacon measurement.
    \item Refactor all of the code for modularity and conciseness.
\end{itemize}